ArKanjo: a tool for detecting function-level Code Duplication in the Linux Kernel

### 2025-06-18 paper/paper.tex
resolve todos

\todo[inline]{colocar no bibtex e usar cite para (Jankowitz, 1988)}
The detection of code duplication, or code clones, has been a research subject for 
decades (Jankowitz, 1988). The literature provides a standard taxonomy, classifying 
clones into four types based on their degree of similarity, from identical copies 
(Type-1) to semantically equivalent but textually different fragments (Type-4)~\cite{litreview}. 
Various detection methodologies have been developed, including textual, token-based, 
tree-based, and graph-based approaches~\cite{litreview}. These have culminated in 
state-of-the-art techniques, such as the graph-based work by Liu et al.~\cite{tailor}. 	
However, the primary focus of such academic work remains on determining whether a given 
pair of code artifacts are duplicates rather than providing a scalable method to scan 
an entire codebase for actionable results. Conversely, existing free software tools explored 
in practice often lack this sophistication, relying instead on primitive textual matching 
that is insufficient for the complexity and scale of the kernel.

@@

\todo[inline]{colocar no bibtex e usar cite para (Svajlenko et al., 2014)}
To validate the capabilities of the ArKanjo tool in finding code duplications using the 
text similarity detection method, we applied two independent
evaluation approaches. The first method assesses the tool using a literature-based approach,
comparing it against the BigCloneBench dataset (Svajlenko et al., 2014). The second
method consists of an empirical analysis of a subset of functions within the AMD Display driver
that our tool identified as duplicates.

To validate the tool against the BigCloneBench dataset \cite{bigclonebench}, we followed
the methodology presented by Liu et al.~\cite{tailor}. We sampled 20{,}000 pairs from each clone
type and added 20{,}000 non-duplicate pairs as negative samples. We applied the same sampling
strategy to our tool to ensure a fair comparison.
Unlike state-of-the-art methods, our tool does not distinguish between clone types and
identifies duplications at the function level rather than the file level, which is typical in
state-of-the-art tools. Therefore, we adapted the metric calculation method for evaluation
purposes. Specifically, we considered every pair of functions with a similarity metric
equal to or greater than a threshold $X$ as duplicates and marked the corresponding file
pairs. A correctly identified duplication pair is counted as accurate for its clone type, while
an incorrectly inferred pair is considered incorrect across all clone types.
To understand the impact of varying the similarity threshold, we evaluated our tool using
different threshold values: 30\%, 40\%, 50\%, 60\%, 70\%, 80\%, 90\%, and 100\%. We then analyzed
and discussed the results.

>>>>

The detection of code duplication, or code clones, has been a research subject for 
decades~\cite{firstman}. The literature provides a standard taxonomy, classifying 
clones into four types based on their degree of similarity, from identical copies 
(Type-1) to semantically equivalent but textually different fragments (Type-4)~\cite{litreview}. 
Various detection methodologies have been developed, including textual, token-based, 
tree-based, and graph-based approaches~\cite{litreview}. These have culminated in 
state-of-the-art techniques, such as the graph-based work by Liu et al.~\cite{tailor}. 	
However, the primary focus of such academic work remains on determining whether a given 
pair of code artifacts are duplicates rather than providing a scalable method to scan 
an entire codebase for actionable results. Conversely, existing free software tools explored 
in practice often lack this sophistication, relying instead on primitive textual matching 
that is insufficient for the complexity and scale of the kernel.

@@

To validate the capabilities of the ArKanjo tool in finding code duplications using the 
text similarity detection method, we applied two independent
evaluation approaches. The first method assesses the tool using a literature-based approach,
comparing it against the BigCloneBench dataset~\cite{bigclonebench}. The second
method consists of an empirical analysis of a subset of functions within the AMD Display driver
that our tool identified as duplicates.

To validate the tool against the BigCloneBench dataset~\cite{bigclonebench}, we followed
the methodology presented by Liu et al.~\cite{tailor}. We sampled 20{,}000 pairs from each clone
type and added 20{,}000 non-duplicate pairs as negative samples. We applied the same sampling
strategy to our tool to ensure a fair comparison.
Unlike state-of-the-art methods, our tool does not distinguish between clone types and
identifies duplications at the function level rather than the file level, which is typical in
state-of-the-art tools. Therefore, we adapted the metric calculation method for evaluation
purposes. Specifically, we considered every pair of functions with a similarity metric
equal to or greater than a threshold $X$ as duplicates and marked the corresponding file
pairs. A correctly identified duplication pair is counted as accurate for its clone type, while
an incorrectly inferred pair is considered incorrect across all clone types.
To understand the impact of varying the similarity threshold, we evaluated our tool using
different threshold values: 30\%, 40\%, 50\%, 60\%, 70\%, 80\%, 90\%, and 100\%. We then analyzed
and discussed the results.
